Parametrization of Neural Networks with Connected Abelian Lie Groups as Data Manifold

### 2020-05-06 llncs2e/paper77.tex
correction

\paragraph{Persistence Landscapes} The persistence landscapes are used for prediction, computed on the persistence diagrams of the datasets cifar10 and cifar100 \citemain{krizhevsky2009learning}, see Fig. \ref{homgroups}. We use the $\alpha$-complex as filtration, see Melodia et al. \citemain{lume}. The maximum $\alpha$-square is set to $e^{12}$. The maximal expansion dimension of the simplicial complex is $10$. The maximal edge length is set to $0.1$. All curves in the mean persistent landscapes are smoothened by a Gaussian filter with $\sigma = 2$.
\input{figure5.tex}

\paragraph{Neural Nets} The data manifold is supposed to be some connected commutative Lie group. We perturb each input vector $\textbf{x}^{(0)}$ with Gaussian noise, such that the input is weighted $0.8 \cdot \textbf{x}^{(0)} + 0.5 \cdot \epsilon$ with $\epsilon \sim \mathcal{N}(0,\sigma^2 \mathbf{I})$. These input vectors are trained to the original vector $\textbf{x}^{(0)}$. We use $\text{L}(\textbf{x}^{(0)}, \textbf{y}) = \frac{1}{n} \sum_{i=1}^{n} \left(\textbf{x}^{(0)}_i-\textbf{y}_i\right)^2$ as loss function. The sigmoid activation function $\sigma(\mathbf{x}^{(l)}) = \frac{1}{1 + e^{-\mathbf{x}^{(l)}}}$ is applied as elementwise activation function throughout the net. In all experiments dense neural nets are used with a bias term. The datasets are flattened from $(32,32,3)$ into $(3072)$. The first layer is applied to the flattened dataset, which is also adapted by back propagation, i.e. $\varphi^{(0)}\left(x^{(0)} \right) =$ $\sigma\left( \sum_{i=1}^{n} \textbf{W}_{ji}^{(1)} \textbf{x}_{i}^{(0)} + \textbf{b}_{i}^{(1)} \right)$. It transfers the data to the desired embedding dimension. The subsequent layers are implemented as $\mathcal{C}^1$-residual invertible layers, see Sect. \ref{resnet} and Sect. \ref{subsec:invertibleneuralnets}. A total of $5$ of these hidden layers are used, all with the same embedding dimension. More details can be found in Appx. \ref{appx:numexp}.

>>>>

\subsubsection*{Persistence Landscapes} The persistence landscapes are used for prediction, computed on the persistence diagrams of the datasets cifar10 and cifar100 \citemain{krizhevsky2009learning}, see Fig. \ref{homgroups}. We use the $\alpha$-complex as filtration, see Melodia et al. \citemain{lume}. The maximum $\alpha$-square is set to $e^{12}$. The maximal expansion dimension of the simplicial complex is $10$. The maximal edge length is set to $0.1$. All curves in the mean persistent landscapes are smoothened by a Gaussian filter with $\sigma = 2$.
\input{figure5.tex}

\subsubsection*{Neural Nets} The data manifold is supposed to be some connected commutative Lie group. We perturb each input vector $\textbf{x}^{(0)}$ with Gaussian noise, such that the input is weighted $0.8 \cdot \textbf{x}^{(0)} + 0.5 \cdot \epsilon$ with $\epsilon \sim \mathcal{N}(0,\sigma^2 \mathbf{I})$. These input vectors are trained to the original vector $\textbf{x}^{(0)}$. We use $\text{L}(\textbf{x}^{(0)}, \textbf{y}) = \frac{1}{n} \sum_{i=1}^{n} \left(\textbf{x}^{(0)}_i-\textbf{y}_i\right)^2$ as loss function. The sigmoid activation function $\sigma(\mathbf{x}^{(l)}) = \frac{1}{1 + e^{-\mathbf{x}^{(l)}}}$ is applied as elementwise activation function throughout the net. In all experiments dense neural nets are used with a bias term. The datasets are flattened from $(32,32,3)$ into $(3072)$. The first layer is applied to the flattened dataset, which is also adapted by back propagation, i.e. $\varphi^{(0)}\left(x^{(0)} \right) =$ $\sigma\left( \sum_{i=1}^{n} \textbf{W}_{ji}^{(1)} \textbf{x}_{i}^{(0)} + \textbf{b}_{i}^{(1)} \right)$. It transfers the data to the desired embedding dimension. The subsequent layers are implemented as $\mathcal{C}^1$-residual invertible layers, see Sect. \ref{resnet} and Sect. \ref{subsec:invertibleneuralnets}. A total of $5$ of these hidden layers are used, all with the same embedding dimension. More details can be found in Appx. \ref{appx:numexp}.
